Four reasons your build is slow

### 2019-01-17 paper.tex
Finish intro.

>>>>

To address this problem, numerous new build systems have been created
(Bazel, Buck, Pants, Aegis, Shake, CMake, Ninja, ...), many purporting
to solve or at least alleviate these problems. However, systems
software ranging from the Linux kernel to LLVM to zlib is still built
with \verb|make| today, suggesting that as in many areas, building new
tools is not sufficient---we must analyze, understand, and improve use
of existing tools as well.

To accomplish this for build systems, we have developed a tool for
analyzing \verb|make|-based builds by instrumenting them while they
run, relying on \verb|make|'s own internal information and the use of
\verb|strace| to analyze the behavior of the actual commands used to
run the build. Our tool computes a dependence graph based on the
actual behavior of the build, then prunes it with data from
\verb|strace|. The resulting graph can accurately predict the
potential parallelism of the build from the instrumentation, show what
build steps cause the biggest slowdown, and answer counterfactual
questions about the results of improving the build system.

After describing our analysis tool, we present four case studies in
reasons software might be slow to build, backed by data and analysis
from our tool. All of the case studies are real, widely-used
open-source projects. In some cases, we identify low-hanging fruit
that can increase the parallelism of a build by 4x; in others we point
to places where code organization changes could make a significant
difference. These case studies demonstrate the benefits of a
build-system analysis tool and point to valuable further investigation.
